---
title: "Project (IE7280 SEC01)"
author: "Haoran Qiu"
date: "4/14/2020"
output: html_document
---

### 1) Clean and normalize data 
```{r}
cancer <- read.csv("~/A.Courses/IE7280 32398/Project/cancer.csv", na.strings="", stringsAsFactors=FALSE)
head(cancer)
summary(cancer)
colnames(cancer)
sapply(cancer, sd)
sum(is.na(cancer))
cancer <- cancer[,-1]
cancer$diagnosis <- as.numeric(c("M" = "1", "B" = "0")[cancer$diagnosis])
```

### 2) Visualize distribution of “diagnosis”
```{r}
library(dplyr)
count_diagnosis <- cancer %>%
  group_by(diagnosis) %>%
  summarise(Count=n())
count_diagnosis$Percentage <- paste(round(count_diagnosis$Count / sum(count_diagnosis$Count) * 100, 2), "%")
count_diagnosis
```
```{r}
library(ggplot2)
png('diagnosis.png', width = 500, height = 500)
cancer%>%
  group_by(diagnosis) %>%
  summarise(Count=n()) %>%
  ggplot(aes(x=reorder(diagnosis, Count), y=Count))+geom_bar(stat="identity")+geom_col(fill="steelblue")+ggtitle("Diagnosis Distribution")+xlab("Diagnosis")+ylab("Count")
```
```{r}
slices <- count_diagnosis$Count
lbls <- c("Benign", "Malignant")
pct <- round(count_diagnosis$Count / sum(count_diagnosis$Count) * 100, 2)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="") # ad % to labels
pie(slices,labels = lbls, col=c("Light Blue", "Pink"), main="Diagnosis Distribution")
```
radius_mean"            
 [3] "texture_mean"           
 [4] "perimeter_mean"         
 [5] "area_mean"              
 [6] "smoothness_mean"        
 [7] "compactness_mean"       
 [8] "concavity_mean"         
 [9] "concave.points_mean"    
[10] "symmetry_mean"          
[11] "fractal_dimension
### 3)	Scatter plots between “mean” columns (to see if there’s any multicollinearity)
```{r}
group <- NA
group[cancer$diagnosis == 0] <- 1
group[cancer$diagnosis == 1] <- 2
my_cols <- c("#00AFBB", "#E7B800") 

png('cancer_scatters.png', width = 1500, height = 1500)
pairs(cancer[,c(2:11)], pch = 19,  cex = 0.5,
      col = my_cols[group])
#The almost perfectly linear patterns between the radius, perimeter and area attributes are hinting at the presence of multicollinearity between these variables. Another set of variables that possibly imply multicollinearity are the concavity, concave_points and compactness.
```

### 4)	Correlations between “mean” columns (to see if there’s any multicollinearity)
```{r}
cancer.cor <- cor(cancer[,c(2:31)])
```
```{r}
library(corrplot)
corrplot(cancer.cor)
```
```{r}
library(ggcorrplot)
png('cancer_cor.png', width = 1000, height = 1000)
ggcorrplot(cancer.cor, hc.order = TRUE, type = "lower", lab = TRUE)
```

### 5)	Drop unnecessary columns based on steps 3) and 4)
```{r}
# first, drop all "worst" columns
cancer_new <- cancer[, -c(22:31)]

# then, drop all columns related to the "perimeter" and "area" attributes
cancer_new <- cancer_new[, -c(4,5,14,15)]

# lastly, drop all columns related to the "concavity" and "concave points" attributes
cancer_new <- cancer_new[, -c(6,7,14,15)]
```

### 6)	Heatmap without dropped columns
```{r}
cancernew.cor <- cor(cancer_new[,c(2:13)])
png('cancer_cor_new.png', width = 800, height = 800)
ggcorrplot(cancernew.cor, hc.order = TRUE, type = "lower", lab = TRUE)
```

### 7)	Split data into training and testing sets
```{r}
train <- cancer_new[1:500,]
test <- cancer_new[501:569,]
```

### 8)	Create a model for the formula
```{r}
model <- glm(diagnosis ~.,family=binomial(link='logit'),data=cancer_new)
summary(model)
```
```{r}
library(finalfit)
library(dplyr)
explanatory <- c("radius_mean", "texture_mean", "smoothness_mean", "compactness_mean", "symmetry_mean", "fractal_dimension_mean", "radius_se", "texture_se", "smoothness_se", "compactness_se", "symmetry_se", "fractal_dimension_se")
dependent <- "diagnosis"
model_table <- cancer_new %>% 
  finalfit(dependent, explanatory, 
  dependent_label_prefix = "")
model_table
```

```{r}
anova(model, test="Chisq")
```
```{r}
library(pscl)
pR2(model)
```

```{r}
fitted.results <- predict(model,newdata=subset(test,select=c(2:13)),type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)
fitted.results
```
```{r}
test$diagnosis
```
```{r}
misClasificError <- mean(fitted.results != test$diagnosis)
print(paste('Accuracy',1-misClasificError))
```

```{r}
library(ROCR)
p <- predict(model, newdata=subset(test,select=c(2:13)), type="response")
pr <- prediction(p, test$diagnosis)
prf <- performance(pr, measure = "tpr", x.measure = "fpr")
png('prf.png', width = 500, height = 500)
plot(prf)
```
```{r}
auc <- performance(pr, measure = "auc")
auc <- auc@y.values[[1]]
auc
```

